\documentclass[10pt,courier]{navymemo}

\author{D Evangelista}
\title{EW496 Course Policy}
\navysubj{Course policy for EW496 (Midshipman Independent Research)}
\navyfiling{1531}
%\navyserial{16-0001}
\date{\today}
%\navymarking{UNCLASSIFIED}

\usepackage{designature}
\usepackage{siunitx}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
%\usepackage{gitinfo2}

\begin{document}
\makedateblock{}

\MEMORANDUM{}

\begin{navyletterheader}
\navyfrom{Assistant Professor D. Evangelista}
\navyto{EW496 advisee, MIDN 1/C S.~Nemani}
\navyskip{}%

\navysubjline{}
\navyskip{}%
\navyref{refa}{ACDEANINST 1531.58 (Administration of Academic Programs)}
\navyref{refb}{WEAPS\&SYSENGRINST 5400.7H (Teaching Methods \& Practices)}
\navyref{refc}{USNANINST 1531.53 (Policies Concerning Graded Academic Work)}
\navyref{refd}{ACDEANINST 1531.79A (Midshipman Research Courses)}
\navyref{refe}{WEAPS\&SYSENGRINST 1530.2G (Midshipman Research Courses Policy)}
%\navyskip{}%
%\navyencl{encl1}{Syllabus, ES200 (Introduction to Systems Engineering), Fall 2016}
\end{navyletterheader}

\section{Requirement}
Per references (\ref{refa}) and (\ref{refb}), this memorandum sets forth my course policy for the Spring 2019 session of EW496 (Midshipman Research).  This information supplements the basic guidance provided in references~(\ref{refa}) through (\ref{refe}). 

\section{Course Objectives and Learning Outcomes}  This is an independent research project on a topic of your choosing and will require significant and focused individual effort to achieve the following:
\subsection{} Develop an understanding of scientific missions for UAS, including planning, logistics, travel, permits and permissions, as well as operations in the field in support of science by planning for a drone mission to be conducted with the device being designed by your capstone EW404 team.
\subsection{} Deploy to Costa Rica and fly UAS missions for science and apply machine vision and machine learning to the resulting imagery to answer ecological questions about endangered sea turtles.   
\subsection{} Connect with scientists outside of USNA to identify design objectives, constraints, functional requirements, and target specifications; and determine is particular mission sets or bundles are more suited to certain airframes or concepts than others (in conjunction with your EW404 work). 
\subsection{} Present work at Biomechanics Seminar. 

\section{Major Deliverables}
\subsection{Proposal} A proposal is required to register for EW496; develop it from your previous ES495 proposal. 
\subsection{Poster and/or talk} A poster or oral presention is required during the Research Poster Session at the end of the term. You are encouraged to present during the Biomechanics Seminar on Thursday after lunch. 
\subsection{Written report} A written report is required at the end of the term. 
\subsection{Drafts} Major deliverables will be routed to me, as well as any outside and cross-project reviewers, for comment in draft form well in advance of the due date, so that you have time to incorporate all comments. 
\subsection{Demonstrations} Plan to demonstrate something at 6 and 12-weeks. 

\section{Additional expectations}  Meetings can be very useful, but are also very costly in terms of person-hours.  Make the world a better place, hold good meetings.  Do not waste your meetings! Use them to create buy-in/consensus and to drive towards decisions and actions.  \textbf{The evening prior} to our weekly meeting, provide an agenda consisting of:
\subsection{} Weekly status covering technical issues, schedule (revised/updated Gantt chart as needed), cost, and approximate hours of effort. 
\subsection{} Biggest current challenge and/or technical question you want to discuss.
\subsection{} For any design decisions / course of actions you want to resolve at the meeting, provide your recommendations along with supporting information.
\subsection{} Written meeting minutes shall be kept documenting who was present, what was discussed, and any decisions or commitments made.  You are also highly encouraged to maintain a design notebook. 
\subsection{} You may opt to use hardcopy, post-it notes on a board, or software tools (Slack, Trello, Asana) for project management; GitHub for code revision control. You are encouraged to use Latex for documents to reduce rework when preparing them for publication. You are required to use Google Team Drive for shared files. Maintaining an online resource (Slack, Trello, Asana) up-to-date counts for providing agenda information the evening prior. 
\subsection{} You may opt to manage your work according to an Agile Project Management method such as Scrum. 

\section{Grading}
Grades will be based on your performance at weekly meetings, my perception of your effort, and demonstrations as agreed upon.  In a
\clearpage
\noindent real engineering project, you will be judged based on on-time delivery of something that meets the requirements, at or under budget, along with complete documentation. The following general guidelines apply: 
\begin{center}
\begin{tabular}{lp{5in}}
A & On time, at or under budget, and meeting performance specs \\
B & Behind, but with a path to completion identified \\
C & Critically behind \\
D & Deficient in performance, execution of tasks, planning, or application of engineering principles \\
F & Let's not go here. \\
\end{tabular}
\end{center}

\noclosing{}\\
%\signspace{}
\noindent\hspace*{4in}\includesignature{}
\signature{D Evangelista}
\sendertitle{Assistant Professor}

\noindent\hspace*{4in}{235 Maury Hall}\\
\hspace*{4in}{(410) 293-6132}\\
\hspace*{4in}{\href{mailto:evangeli@usna.edu}{evangeli@usna.edu}}

\copyto{}
File\\
Course coordinator


% record note
\navyrecordnote
\thispagestyle{empty}

\navyrecordnotedistribution{%
Evangelista\\%
Jaramillo}
%\navyrecordnoteconcurrences{%
%\navyrecordnoteconcurrence{08K}
%\navyrecordnoteconcurrence{08I}}

\navyrecordnotesubjline

\section{} This memo provides course policies for Evangelista's Spring 2019 EW496 Midshipman Independent Research effort by Nemani.

\section{} Nemani will be planning for drone missions in support of science including the planned deployment to Costa Rica in March 2019.  

\section{}  The policies here are adapted from those provided by CDR Severson for ES404.  

\end{document}


