\documentclass[10pt,courier]{navymemo}

\newcommand{\myroot}{../..}
\usepackage{\myroot/es495}

\author{\usnaInstructorShort}
\title{\usnaCourseNumber\ Course Policy}
\navysubj{Course policy for \usnaCourseNumber\ (\usnaCourseName)}
\navyfiling{1531}
%\navyserial{16-0001}
\date{3 SEP 2018}
%\navymarking{UNCLASSIFIED}

\usepackage{designature}
\usepackage{siunitx}

\begin{document}
\makedateblock{}

\MEMORANDUM{}

\begin{navyletterheader}
\navyfrom{Assistant Professor L.~Devries}
\navyfrom{Assistant Professor D.~Evangelista}
\navyto{\usnaCourseNumber\ advisee, MIDN 1/C M.~Descour}
\navyskip{}%

\navysubjline{}
\navyskip{}%
\navyref{refa}{ACDEANINST 1531.58 (Administration of Academic Programs)}
\navyref{refb}{WEAPS\&SYSENGRINST 5400.7H (Teaching Methods \& Practices)}
\navyref{refc}{USNANINST 1531.53 (Policies Concerning Graded Academic Work)}
\navyref{refd}{ACDEANINST 1531.79A (Midshipman Research Courses)}
\navyref{refe}{WEAPS\&SYSENGRINST 1530.2G (Midshipman Research Courses Policy)}
%\navyskip{}%
%\navyencl{encl1}{Syllabus, ES200 (Introduction to Systems Engineering), Fall 2016}
\end{navyletterheader}

\section{Requirement}
Per references (\ref{refa}) and (\ref{refb}), this memorandum sets forth my course policy for the \courseTerm\ session of \usnaCourseNumber\ (\usnaCourseName, 0-6-3).  This information supplements the basic guidance provided in references~(\ref{refa}) through (\ref{refe}). 

\section{Course Objectives and Learning Outcomes}  This is an independent research project on a topic of your choosing and will require significant and focused individual effort to achieve the following, which you proposed as your Honors Capstone project:
\subsection{} Quantify leech locomotion, including measuring frequencies, wavelengths, patterns of movement and gaits, using video or live observation as necessary, and identify mechanisms in nature for achieving and controlling similar movement. This could include use of a maze or obstacle course and examination of different modes of locomotion used in water versus on land, or along surfaces, etc. 
\subsection{} Quantify leech attachment force, and identify mechanisms in nature used for attachment/detachment in a similar manner.  
\subsection{} Develop soft-bodied robotic concepts that bend and twist with sufficient speed and range to achieve leech-like locomotion. 
\subsection{} Develop end attachment concepts with sufficient force and speed of attachment/detachment comparable to actual leeches. 
\subsection{} Present preliminary work to scientists at a conference, notionally the 2019 Society for Integrative and Comparative Biology conference. 

\section{Major Deliverables}
\subsection{Proposal} A proposal is required to register for ES495. 
\subsection{Poster and/or talk} A poster or oral presention is required during the Research Poster Session at the end of the term. In addition, you are encouraged to present the work at the SICB conference in January 2019. 
\subsection{Written report} A written report is required at the end of the term; this will constitute a draft or major section of your final Capstone report. 
\subsection{Drafts} Major deliverables will be routed to your advisors, as well as any outside and cross-project reviewers, for comment in draft form well in advance of the due date, so that you have time to incorporate all comments. 
\subsection{Demonstrations} Plan to demonstrate something at 6 and 12-weeks. 

\section{Additional expectations}  Meetings can be very useful, but are also very costly in terms of person-hours.  Make the world a better place, hold good meetings.  Do not waste your meetings! Use them to create buy-in/consensus and to drive towards decisions and actions.  \textbf{The evening prior} to our weekly meeting, provide an agenda consisting of:
\subsection{} Weekly status covering technical issues, schedule (revised/updated Gantt chart as needed), cost, and approximate hours of effort. 
\subsection{} Biggest current challenge and/or technical question you want to discuss.
\subsection{} For any design decisions / course of actions you want to resolve at the meeting, provide your recommendations along with supporting information.
\subsection{} Written meeting minutes shall be kept documenting who was present, what was discussed, and any decisions or commitments made.  You are also highly encouraged to maintain a design notebook. 
\subsection{} You may opt to use hardcopy, post-it notes on a board, or software tools (Slack, Trello, Asana) for project management; GitHub for code revision control. You are encouraged to use Latex for documents to reduce rework when preparing them for publication. You are required to use Google Team Drive for shared files. Maintaining an online resource (Slack, Trello, Asana) up-to-date counts for providing agenda information the evening prior. 
\subsection{} You may opt to manage your work according to an Agile Project Management method such as Scrum. 

\clearpage
\section{Grading}
Grades will be based on your performance at weekly meetings, my perception of your effort, and demonstrations as agreed upon.  In a real engineering project, you will be judged based on on-time delivery of something that meets the requirements, at or under budget, along with complete documentation. The following general guidelines apply: 
\begin{center}
\begin{tabular}{lp{5in}}
A & On time, at or under budget, and meeting performance specs \\
B & Behind, but with a path to completion identified \\
C & Critically behind \\
D & Deficient in performance, execution of tasks, planning, or application of engineering principles \\
F & Let's not go here. \\
\end{tabular}
\end{center}

\noclosing{}\\
\signspace{}
%\noindent\hspace*{4in}\includesignature{}
\signature{D Evangelista}
\sendertitle{Assistant Professor}
\noindent\hspace*{4in}{235 Maury Hall}\\
\hspace*{4in}{\href{mailto:evangeli@usna.edu}{evangeli@usna.edu}}

\copyto{}
File\\
Course coordinator


% record note
\navyrecordnote
\thispagestyle{empty}

\navyrecordnotedistribution{%
Evangelista(w)\\%
Devries(w)\\
Jaramillo(w)}
\navyrecordnoteconcurrences{%
\navyrecordnoteconcurrence{Devries}}
%\navyrecordnoteconcurrence{08I}}

\navyrecordnotesubjline

\section{} This memo provides course policies for Descour's Fall 2019 ES495 Midshipman Independent Research efforts, as part of his honors capstone project.

\section{} Descour is developing soft-bodied robots based on leeches.  

\section{} The policies here are adapted from those provided by CDR Severson for ES404.  

\end{document}


