\documentclass[10pt,courier]{navymemo}

\author{D Evangelista}
\title{EW495 Course Policy}
\navysubj{Course policy for EW495 (Midshipman Independent Research) for MIDN 1/c Marcello}
\navyfiling{1531}
%\navyserial{16-0001}
\date{\today}
%\navymarking{UNCLASSIFIED}

\usepackage{designature}
\usepackage{siunitx}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
%\usepackage{gitinfo2}

\begin{document}
\makedateblock{}

\MEMORANDUM{}

\begin{navyletterheader}
\navyfrom{Assistant Professor D. Evangelista}
\navyto{EW495 advisee, MIDN 1/C E.~Marcello}
\navyskip{}%

\navysubjline{}
\navyskip{}%
\navyref{refa}{ACDEANINST 1531.58 (Administration of Academic Programs)}
\navyref{refb}{WEAPS\&SYSENGRINST 5400.7H (Teaching Methods \& Practices)}
\navyref{refc}{USNANINST 1531.53 (Policies Concerning Graded Academic Work)}
\navyref{refd}{ACDEANINST 1531.79A (Midshipman Research Courses)}
\navyref{refe}{WEAPS\&SYSENGRINST 1530.2G (Midshipman Research Courses Policy)}
%\navyskip{}%
%\navyencl{encl1}{Syllabus, ES200 (Introduction to Systems Engineering), Fall 2016}
\end{navyletterheader}

\section{Requirement}
Per references (\ref{refa}) and (\ref{refb}), this memorandum sets forth my course policy for the Fall 2019 session of EW495 (Midshipman Research).  This information supplements the basic guidance provided in references~(\ref{refa}) through (\ref{refe}). 

\section{Course Objectives and Learning Outcomes}  This is an independent research project on a topic of your choosing and will require significant and focused individual effort to achieve the following:
\subsection{} Make reasonable progress towards honors capstone completion
\subsection{} Identify rational criteria for scaling extreme maneuvers appropriately to the space and limitations of the hardware at hand
\subsection{} Develop control algorithms for performing extreme maneuvers in quadrotors, including theory, analytical solutions, numerical simulation, and/or experimental data
\subsection{} Present work at Biomechanics Seminar, the USNA Fall Research Poster Session, and/or a suitable academic conference. 
\subsection{} As a stretch goal, consider examination of other extreme maneuvers observed in animal behavior, or of bio-inspired maneuvering strategies used to clear difficult obstacles. 

\section{Major Deliverables}
\subsection{Poster and/or talk} A poster or oral presention is required during the Research Poster Session at the end of the term. You are encouraged to present during the Biomechanics Seminar on Thursday after lunch. 
\subsection{Written report} A written report is required at the end of the term. 
\subsection{Drafts} Major deliverables will be routed to me, as well as any outside and cross-project reviewers, for comment in draft form well in advance of the due date, so that you have time to incorporate all comments. 
\subsection{Demonstrations} Plan to demonstrate something at 6 and 12-weeks and end of term. 

\clearpage
\section{Additional expectations} You are your own program manager. Manage your program aggressively!
\subsection{} The priority if for you to get things done and to get the support you need. If your work is proceeding and you wish to use meeting time to work, that is acceptable so long as you keep me informed. 
\subsection{} Meetings can be very useful, but are also very costly in terms of person-hours.  Make the world a better place, hold good meetings.  Do not waste your meetings! Use them to create buy-in/consensus and to drive towards decisions and actions, and use other channels (e.g. Slack, Trello) to accomplish the mundane and less important things.
\subsection{} Focus meetings by identifying up front (and preferably with an agenda and read ahead material provided the night before the meeting) the biggest current challenge and/or technical question you want to discuss. Also, for any design decisions / course of actions you want to resolve at the meeting, provide your recommendations along with supporting information. Written meeting minutes shall be kept documenting who was present, what was discussed, and any decisions or commitments made.  
\subsection{} We will manage your work according to an Agile Project Management method such as Scrum. You may opt to use hardcopy, post-it notes on a board, or software tools (Slack, Trello, Asana) for project management.   Maintaining an online resource (Slack, Trello, Asana) up-to-date counts for providing agenda information the evening prior to meetings. 
\subsection{} You are required to use Google Team Drive for shared files, GitHub for code revision control. Major deliverables shall use Latex for documents, to reduce rework when preparing them for publication.

\section{Use of templates from third parties} Please do not use any templates, example reports, or example budgets from other third parties without first discussing with me. These are not normally suited to the types of projects my students do, and result in wasted time and diluted efforts that are irrelevant to the questions at hand. 

\section{Grading}
Grades will be based on your performance at weekly meetings, my perception of your effort, and demonstrations as agreed upon.  In a
\clearpage\noindent real engineering project, you will be judged based on on-time delivery of something that meets the requirements, at or under budget, along with complete documentation. The following general guidelines apply: 
\begin{center}
\begin{tabular}{lp{5in}}
A & On time, at or under budget, and meeting performance specs \\
B & Behind, but with a path to completion identified \\
C & Critically behind \\
D & Deficient in performance, execution of tasks, planning, or application of engineering principles \\
F & Let's not go here. \\
\end{tabular}
\end{center}

\noclosing{}\\
%\signspace{}
\noindent\hspace*{4in}\includesignature{}
\signature{D Evangelista}
\sendertitle{Assistant Professor}

\noindent\hspace*{4in}{207 Maury Hall}\\
\hspace*{4in}{(410) 293-6132}\\
\hspace*{4in}{\href{mailto:evangeli@usna.edu}{evangeli@usna.edu}}

\copyto{}
File\\
MIDN 1/c Credle\\
Course coordinator


% record note
\navyrecordnote
\thispagestyle{empty}

\navyrecordnotedistribution{%
Evangelista%
}
%\navyrecordnoteconcurrences{%
%\navyrecordnoteconcurrence{08K}
%\navyrecordnoteconcurrence{08I}}

\navyrecordnotesubjline

\section{} This memo provides course policies for Marcello's Fall 2019 EW495 Midshipman Independent Research effort.

\section{} Marcello's honors project is to fly extreme maneuvers with quadrotors, notionally patterned after Anna's Hummingbird display dives, though any progress on bio-inspired maneuvering strategies (aerial righting, clearances of obstacles and apertures, performance in turbulence, advesarial maneuvers, dances or displays) would also be welcome. 

\section{}  The policies here are adapted from those provided by CAPT Severson for ES404.  
\end{document}


