\documentclass[10pt,courier]{navymemo}

\author{D Evangelista}
\title{EW404 Course Policy}
\navysubj{Course policy for EW404 (Robotics and Control Engineering Capstone) for MIDN 1/c Carroll, Kang, Lim, Phan and MIDN 2/c Hofland}
\navyfiling{1531}
%\navyserial{16-0001}
\date{6 Sep 2019}
%\navymarking{UNCLASSIFIED}

\usepackage{designature}
\usepackage{siunitx}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
%\usepackage{gitinfo2}

\begin{document}
\makedateblock{}

\MEMORANDUM{}

\begin{navyletterheader}
\navyfrom{Assistant Professor D. Evangelista}
\navyto{EW404 advisees, MIDN 1/C Carroll, Kang, Lim, Phan and MIDN 2/c Hofland}
\navyskip{}%

\navysubjline{}
\navyskip{}%
\navyref{refa}{ACDEANINST 1531.58 (Administration of Academic Programs)}
\navyref{refb}{WEAPS\&SYSENGRINST 5400.7H (Teaching Methods \& Practices)}
\navyref{refc}{USNANINST 1531.53 (Policies Concerning Graded Academic Work)}
\navyref{refd}{ACDEANINST 1531.79A (Midshipman Research Courses)}
\navyref{refe}{WEAPS\&SYSENGRINST 1530.2G (Midshipman Research Courses Policy)}
%\navyskip{}%
%\navyencl{encl1}{Syllabus, ES200 (Introduction to Systems Engineering), Fall 2016}
\end{navyletterheader}

\section{Requirement}
Per references (\ref{refa}) and (\ref{refb}), this memorandum sets forth my course policy for Fall 2019 / AY2020 Biomechanics Capstone Team.  This information supplements the basic guidance provided in references~(\ref{refa}) through (\ref{refe}). 

\section{Course Objectives and Learning Outcomes}  This is an independent research project on a topic of your choosing and will require significant and focused individual effort to achieve the following:
\subsection{} Complete a sufficiently interesting capstone project that you will be proud to present on Capstone Day as work qualifying you to graduate
\subsection{} Develop or adapt an unmanned aerial system and payloads for accomplishing a mission of your choosing, including sensors, actuators, and manipulators
\subsection{} Develop machine vision algorithms for identifying organisms or features of interest as part of your mission
\subsection{} Develop algorithms for autonomous navigation during your mission, as well as any necessary manual backup procedures, startup, shutdown, or controlled maintenance to support. 
\subsection{} Arrange logistics for the deployment of your design and its use in the field to complete your desired mission
\subsection{} Work with a science and/or military customer
\subsection{} Present work at Biomechanics Seminar, Capstone Day, and/or a suitable academic conference. 

\section{Major Deliverables}
\subsection{Concept and preliminary design reviews} As directed in EW401
\subsection{Bench demonstration} Suitable completion of appropriately aggressive sprint tasks should qualify as necessary EW401 bench demonstrations
\subsection{Poster and talk} A poster and oral presention is required on Capstone Day. You are encouraged to present in the spring during the Biomechanics Seminar on Thursday after lunch, as preparation for Capstone Day.
\subsection{Written report} A written report is required at the end of the Spring 2020. 
\subsection{Drafts} Major deliverables will be routed to me, as well as any outside and cross-project reviewers, for comment in draft form well in advance of the due date, so that you have time to incorporate all comments. 
\subsection{Demonstrations} Plan to demonstrate something at 6 and 12-weeks and end of term. 

\section{Additional expectations} You are your own program manager. Manage your program aggressively!
\subsection{} Meetings can be very useful, but are also very costly in terms of person-hours.  Make the world a better place, hold good meetings.  Do not waste your meetings! Use them to create buy-in/consensus and to drive towards decisions and actions, and use other channels (e.g. Slack, Trello) to accomplish the mundane and less important things.
\subsection{} Focus meetings by identifying up front (and preferably with an agenda and read ahead material provided the night before the meeting) the biggest current challenge and/or technical question you want to discuss. Also, for any design decisions / course of actions you want to resolve at the meeting, provide your recommendations along with supporting information. Written meeting minutes shall be kept documenting who was present, what was discussed, and any decisions or commitments made.  
\subsection{} We will manage your work according to an Agile Project Management method such as Scrum. You may opt to use hardcopy, post-it notes on a board, or software tools (Slack, Trello, Asana) for project management.   Maintaining an online resource (Slack, Trello, Asana) up-to-date counts for providing agenda information the evening prior to meetings. 
\subsection{} In EW404, you will be required to use Google Team Drive for shared files, GitHub for code revision control. Major deliverables shall use Latex for documents, to reduce rework when preparing them for publication.
\subsection{} At the conclusion of EW404, you will be required to outbrief, including proper disposition of all data and materials and a turnover with any underclass planning to continue with biomechanics capstones in AY2021. 

\section{Use of templates from third parties} Please do not use any templates, example reports, or example budgets from other third parties without first discussing with me. These are not normally suited to the types of projects my students do, and result in wasted time and diluted efforts that are irrelevant to the questions at hand. 
\subsection{} Previous capstone EW401 budgets have been insufficient detail and scope and provided too late to seriously support doing work in the field. We will need some improvement here. 
\subsection{} Your ultimate report for EW404 will need to recognize that your customer is a scientist and that your report is shaped for scientific publication of the driving research questions, methods (including engineering design of your system), mission results, and discussion of scientific findings.


\section{Grading in EW404}
In EW404, grades will be based on your performance at weekly meetings, my perception of your effort, and demonstrations as agreed upon.  In a real engineering project, you will be judged based on on-time delivery of something that meets the requirements, at or under budget, along with complete documentation. The following general guidelines apply: 
\begin{center}
\begin{tabular}{lp{5in}}
A & On time, at or under budget, and meeting performance specs \\
B & Behind, but with a path to completion identified \\
C & Critically behind \\
D & Deficient in performance, execution of tasks, planning, or application of engineering principles \\
F & Let's not go here. \\
\end{tabular}
\end{center}

\noclosing{}\\
%\signspace{}
\noindent\hspace*{4in}\includesignature{}
\signature{D Evangelista}
\sendertitle{Assistant Professor}

\noindent\hspace*{4in}{207 Maury Hall}\\
\hspace*{4in}{(410) 293-6132}\\
\hspace*{4in}{\href{mailto:evangeli@usna.edu}{evangeli@usna.edu}}

\copyto{}
File\\
EW401 instructor\\
MIDN 1/c Credle, Marcello\\
EW404 course coordinator


% record note
\navyrecordnote
\thispagestyle{empty}

\navyrecordnotedistribution{%
Evangelista\\
Webster-Giddings (w)%
}
\navyrecordnoteconcurrences{%
\navyrecordnoteconcurrence{EW401 Instructor}}


\navyrecordnotesubjline

\section{} This memo provides course policies (advanced version, for information) for the AY2020 Biomechanics Capstone Team. These will be come formally applicable once the team starts EW404 in Spring 2020. 

\section{} The team has settled on a science mission to perform botanical surveys or sample return using UAS. 

\section{}  The policies here are adapted from those provided by CAPT Severson for ES404.  
\end{document}


